---
title: "Corona virus"
---

A coronavirus called COVID-19 has affected this world in 2020. The infection spread globally and was declared a pandemic.

Several countries have decided to take unprecedented and severe precautions to prevent the spread of this virus.

Among these are social distancing and lockdowns. These cause people to stay at home and work from home. In addition school, university and pre school closings result in children being at home.


```{r setup, echo=FALSE,include=FALSE,warning = FALSE}
rm(list = ls())
#library(libwgeom)
#install.packages("googleway")
library(googleway)
library(purrr)
library(sf)
library(cowplot)
#install.packages("ggspatial")
library(ggspatial)
#install.packages("rnaturalearth")
#install.packages("rnaturalearthdata")
library(rnaturalearth)
library(rnaturalearthdata)
library(cowplot)

#install.packages('rgeos')
library(rgeos)
#install.packages('tools')
library(tools)
#install.packages("ggiraph")
library(ggiraph)
library(ggrepel)
#install.packages("maps")
library(maps)
library(plyr)
library(dplyr)
library(httr)
library(rvest)


```

Sectors:
```{r box1, echo=FALSE,warning = FALSE,include=FALSE}

SPsec_N <- c('Technology','Health Care','Financials','Consumer Discretionary','Communication Services','Industrials','Consumer Staples',
             'Materials','Real Estate','Utilities','Energy')
SPsec <- c('XLK','XLV','XLF','XLY','XLC','XLI','XLP','XLB','XLRE','XLU','XLE')


library(BatchGetSymbols)
library(ggplot2)
library(data.table)
library(quantmod)
library(plyr)
library(dplyr)
library(ggiraph)

time <- Sys.time()


first.date <- '2020-01-01'
last.date <- Sys.Date()
freq.data <- 'daily'

l.out <- BatchGetSymbols(tickers = SPsec, #all, #tickers2, 
                         first.date = first.date,
                         last.date = last.date, 
                         freq.data = freq.data,
                         cache.folder = file.path(tempdir(), 
                                                  'BGS_Cache') ) # cache in tempdir()



ticks <- l.out$df.tickers
colms <- c('price.close', 'ticker', 'ref.date')
ticksdf <- ticks[colms]
colnames(ticksdf) <- c('Price' ,'ticker','Date' )

#combine Gold and ticker data to express price relative to gold and hyg
ticksdf <- ticksdf[order(as.Date(ticksdf$Date, format="%Y-%m/%d")),]
#ticksdf1 <- subset(ticksdf, ticker=='AAPL')



no_tick <- unique(ticksdf$ticker)
ticksdf4 <- NULL

for (i in seq_along(no_tick)) {
  ticker5 <- no_tick[i]
  ticksdf5 <- subset(ticksdf, ticker==ticker5)
  # ticksdf5 <-ticksdf5[-c(1:22),]
  ticksdf5$rel_change <- (ticksdf5$Price/ticksdf5$Price[1])*100
  ticksdf4 <- rbind.fill(ticksdf4, ticksdf5)
}
ticksdf4$category <- 0
for (i in seq_along(SPsec_N)) {
  
  ticksdf4$category <- ifelse(!ticksdf4$ticker == SPsec[i], 
                               ticksdf4$category, SPsec_N[i])
}
p10 <- ggplot(ticksdf4, aes(x = Date, y = rel_change, color=category))+
geom_line() + ylab('Sectors since begin of 2020') + xlab('')+
ggthemes::theme_economist()+
theme(legend.title = element_blank())

my_gg <- p10 + geom_line_interactive(aes(tooltip = category), size = 0.5) 



```

```{r plotbox, echo=FALSE,warning = FALSE}
girafe(code = print(my_gg) )
```

Country indices in the last 10 years:

```{r box2, echo=FALSE,warning = FALSE,include=FALSE}

country_N <- c('Philippines','Brazil','South Africa','India','DEVworld','world','China','ChinaTech','Germany','UK','Europe','Japan')
country <- c('EPHE','EWZ','EZA','INDA','URTH','ACWI','FXI','KWEB','EWG','EWU','VGK','EWJ')


library(BatchGetSymbols)
library(ggplot2)
library(data.table)
library(quantmod)
library(plyr)
library(dplyr)
library(ggiraph)

time <- Sys.time()


first.date <- '2010-01-01'
last.date <- Sys.Date()
freq.data <- 'weekly'

l.out <- BatchGetSymbols(tickers = country, #all, #tickers2, 
                         first.date = first.date,
                         last.date = last.date, 
                         freq.data = freq.data,
                         cache.folder = file.path(tempdir(), 
                                                  'BGS_Cache') ) # cache in tempdir()



ticks <- l.out$df.tickers
colms <- c('price.close', 'ticker', 'ref.date')
ticksdf <- ticks[colms]
colnames(ticksdf) <- c('Price' ,'ticker','Date' )

#combine Gold and ticker data to express price relative to gold and hyg
ticksdf <- ticksdf[order(as.Date(ticksdf$Date, format="%Y-%m/%d")),]
#ticksdf1 <- subset(ticksdf, ticker=='AAPL')



no_tick <- unique(ticksdf$ticker)
ticksdf4 <- NULL

for (i in seq_along(no_tick)) {
  ticker5 <- no_tick[i]
  ticksdf5 <- subset(ticksdf, ticker==ticker5)
  # ticksdf5 <-ticksdf5[-c(1:22),]
  ticksdf5$rel_change <- (ticksdf5$Price/ticksdf5$Price[1])*100
  ticksdf4 <- rbind.fill(ticksdf4, ticksdf5)
}
ticksdf4$category <- 0
for (i in seq_along(country_N)) {
  
  ticksdf4$category <- ifelse(!ticksdf4$ticker == country[i], 
                               ticksdf4$category, country_N[i])
}
p11 <- ggplot(ticksdf4, aes(x = Date, y = rel_change, color=category))+
geom_line() + ylab('Country stock markets since begin of 2020') + xlab('')+
ggthemes::theme_economist()+
theme(legend.title = element_blank())

my_gg2 <- p11 + geom_line_interactive(aes(tooltip = category), size = 0.3) 



```

```{r plotbox2, echo=FALSE,warning = FALSE}
girafe(code = print(my_gg2) )
```

Countries in 2020:



```{r box3, echo=FALSE,warning = FALSE,include=FALSE}

country_N <- c('Philippines','Brazil','South Africa','India','DEVworld','world','China','ChinaTech','Germany','UK','Europe','Japan')
country <- c('EPHE','EWZ','EZA','INDA','URTH','ACWI','FXI','KWEB','EWG','EWU','VGK','EWJ')


library(BatchGetSymbols)
library(ggplot2)
library(data.table)
library(quantmod)
library(plyr)
library(dplyr)
library(ggiraph)

time <- Sys.time()


first.date <- '2020-01-01'
last.date <- Sys.Date()
freq.data <- 'daily'

l.out <- BatchGetSymbols(tickers = country, #all, #tickers2, 
                         first.date = first.date,
                         last.date = last.date, 
                         freq.data = freq.data,
                         cache.folder = file.path(tempdir(), 
                                                  'BGS_Cache') ) # cache in tempdir()



ticks <- l.out$df.tickers
colms <- c('price.close', 'ticker', 'ref.date')
ticksdf <- ticks[colms]
colnames(ticksdf) <- c('Price' ,'ticker','Date' )

#combine Gold and ticker data to express price relative to gold and hyg
ticksdf <- ticksdf[order(as.Date(ticksdf$Date, format="%Y-%m/%d")),]
#ticksdf1 <- subset(ticksdf, ticker=='AAPL')



no_tick <- unique(ticksdf$ticker)
ticksdf4 <- NULL

for (i in seq_along(no_tick)) {
  ticker5 <- no_tick[i]
  ticksdf5 <- subset(ticksdf, ticker==ticker5)
  # ticksdf5 <-ticksdf5[-c(1:22),]
  ticksdf5$rel_change <- (ticksdf5$Price/ticksdf5$Price[1])*100
  ticksdf4 <- rbind.fill(ticksdf4, ticksdf5)
}
ticksdf4$category <- 0
for (i in seq_along(country_N)) {
  
  ticksdf4$category <- ifelse(!ticksdf4$ticker == country[i], 
                               ticksdf4$category, country_N[i])
}
p11 <- ggplot(ticksdf4, aes(x = Date, y = rel_change, color=category))+
geom_line() + ylab('Country stock markets since begin of 2020') + xlab('')+
ggthemes::theme_economist()+
theme(legend.title = element_blank())

my_gg2 <- p11 + geom_line_interactive(aes(tooltip = category), size = 0.5) 



```

```{r plotbox3, echo=FALSE,warning = FALSE}
girafe(code = print(my_gg2) )
```



```{r box4, echo=FALSE,warning = FALSE,include=FALSE}
setwd('~/Google Drive/algotrading/robinhood')
RH_fund500 <- read.csv("RH_fund5002020-05-29.csv")
library(ggplot2)
library(ggiraph)
RH_fun <-ggplot()+
  geom_point_interactive(data=RH_fund500,aes(x=pb_ratio,y=pe_ratio, color=sector,tooltip = symbol,size=dividend_yield),alpha=0.2)+
  xlim(c(0,2))+
  ylim(c(0,100))+
  ggtitle('PB vs.PE ratio of S&P 500 stocks')
  #ggrepel::geom_text_repel(data = RH_fund500,aes(x=pb_ratio,y=pe_ratio,label=sector))

```


```{r plotbox4, echo=FALSE,warning = FALSE}
girafe(code = print(RH_fun) )
```
