---
title: "Postdoctoral fellowships"
output:
  html_document:
    df_print: paged
  pdf_document: default
---



```{r setup, echo=FALSE,include=FALSE,warning = FALSE}
rm(list = ls())
#https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_html.html
#install.packages("kableExtra")
#library(libwgeom)
#install.packages("googleway")
library(googleway)
library(knitr)
library(purrr)
library(sf)
library(cowplot)
#install.packages("ggspatial")
library(ggspatial)
#install.packages("rnaturalearth")
#install.packages("rnaturalearthdata")
library(rnaturalearth)
library(rnaturalearthdata)
library(cowplot)
library(kableExtra)
#install.packages('rgeos')
library(rgeos)
#install.packages('tools')
library(tools)
#install.packages("ggiraph")
library(ggiraph)
library(ggrepel)
#install.packages("maps")
library(maps)
library(plyr)
library(dplyr)
library(httr)
library(rvest)
library(magrittr)
setwd('~/website')
fellow <- read.csv('_Postdoc_Funding.csv')
#potential addtl. fellowships
#https://www.bwfund.org/programs-offered
#https://www.fraxa.org/fragile-x-research/grant-application/
#https://pva.org/research-resources/research-foundation/
#https://www.daad.org/en/find-funding/phd-postdocs/postdoctoral-researchers-international-mobility-experience-p-r-i-m-e/
#https://grants.nih.gov/grants/funding/ac_search_results.htm?text_curr=f05&Search.x=0&Search.y=0&Search_Type=Activity
#https://www.eacr.org/content/jobs.php
#http://leader.unisannio.it/scholarships.html
#https://www.embo.org/funding-awards/fellowships/postdoctoral-fellowships#eligibility
#https://www.embo.org/funding-awards/fellowships/postdoctoral-fellowships/embo-long-term-fellowship-awards
#https://www.cirm.ca.gov/researchers/funding-opportunities
#https://www.dfg.de/foerderung/programme/einzelfoerderung/walter_benjamin/index.html
#https://www.dfg.de/foerderung/programme/einzelfoerderung/forschungsstipendien/
#https://dceg.cancer.gov/fellowship-training/become-a-fellow/research-training-areas/oeeb-specific-investigators
#https://www.profellow.com/fellowships/27-postdoctoral-fellowships-in-medicine-and-public-health/
#https://www.embl.de/training/postdocs/06-funding_opportunities/
#https://engelhorn-stiftung.de/index.php/stipendium-bewerbung.php deutschsprachiger raum
#https://www.fritz-thyssen-stiftung.de/foerderung/foerderarten/postdoc-stipendien/
#https://ec.europa.eu/research/mariecurieactions/actions/individual-fellowships_en
#https://www.aesnet.org/research/funding%20for%20junior%20investigators/Post-Doctoral%20Research%20Fellowships
#https://www.dfg.de/en/research_funding/programmes/individual/emmy_noether/index.html
#https://www.toyotafound.or.jp/english/special/2020/

fellow2 <- data.frame('Fellowship'=c('Phrma Foundation',
                                     'Jane Coffins Child',
                                     'Life Sciences Research Foundation',
                                     'Damon Runyon Cancer Research Foundation',
                                     'Crohns Colitis Foundation',
                                     'National Multiple Sclerosis Society',
                                     'JSM Foundation',
                                     'American Heart Association',
                                     'JDRF',
                                     'Cancer Research Institute',
                                     'New York Stem cell Foundation',
                                     'American Diabetes Association',
                                     'Helen Hay Whitney Foundation',
                                     'American Society of Nephrology',
                                     'Molecular Science Software Institute',
                                     'K99 NIH',
                                     'American Association for Cancer Research',
                                     'Childrens Tumor Foundation',
                                     'American Brain Tumor Association',
                                     'Lalor Foundation (Reproductive Health)',
                                     'Health Reseource in Action (Basic Science)',
                                     'National Hemophilia Foundation',
                                     'American Federation for Aging Research',
                                     'American Parkinson Diseases Association',
                                     'Parkinsons Foundation',
                                     'Prostatate Cancer Foundation',
                                     'Herediary Disease Foundation',
                                     'Cystic Fibrosis Foundation',
                                     'Hope Funds for Cancer Research'
  
),

'Awards_2019'=c(51,30,27,20,NA,NA,9,255,12,19,
                             4,31,24,10,15,160,51,4,6,10,
                             7,2,20,3,5,28,7,NA,3),


'contact'=c('foundation@phrma.org','jccfund@yale.edu','direnzo@lsrf.org','awards@damonrunyon.org','grant@crohnscolitisfoundation.org',
            'Douglas.Landsman@nmss.org','info@jsmf.org','apply@heart.org','preawardsupport@jdrf.org','grants@cancerresearch.org',
             'fellowship@nyscf.org','grantquestions@diabetes.org','office@hhwf.org','grants@asn-online.org','info@molssi.org',
            'healthinfo@niddk.nih.gov','aacr@aacr.org','grants@ctf.org','info@abta.org','fellowshipmanager@gmafoundations.com',
            'lcarver@hria.org','mwitkop@hemophilia.org','afarapplication@afar.org','hgray@apdaparkinson.org','grants@parkinson.org',
            'info@pcf.org','cures@hdfoundation.org', 'grants@cff.org','grants@hope-funds.org'),

'Link'=c( sprintf("window.open(\"%s%s\")",'http://www.phrmafoundation.org/2018-awards/post-doctoral-fellowships', as.character('/')),
          sprintf("window.open(\"%s%s\")",'https://www.jccfund.org/fellowship-information', as.character('/')),
          sprintf("window.open(\"%s%s\")",'http://www.lsrf.org/apply.htm', as.character('l')),
          sprintf("window.open(\"%s%s\")",'https://www.damonrunyon.org/for-scientists/award-programs', as.character('/')),
          sprintf("window.open(\"%s%s\")",'https://www.crohnscolitisfoundation.org/research/grants-fellowships/research-fellowship-awards', as.character('/')),
          sprintf("window.open(\"%s%s\")",'https://www.nationalmssociety.org/For-Professionals/Researchers/Society-Funding/Training-Grants-and-Fellowships/Postdoctoral-Fellowships', as.character('/')),
          sprintf("window.open(\"%s%s\")",'https://www.jsmf.org/apply/fellowship', as.character('/')),
          sprintf("window.open(\"%s%s\")",'https://professional.heart.org/professional/ResearchPrograms/ApplicationInformation/UCM_443314_Postdoctoral-Fellowship.jsp', as.character('/')),
          sprintf("window.open(\"%s%s\")",'http://grantcenter.jdrf.org/rfa/postdoctoral-fellowships', as.character('/')),
          sprintf("window.open(\"%s%s\")",'http://www.cancerresearch.org/scientists/fellowships-grants/post-doctoral-fellows', as.character('/')),
          sprintf("window.open(\"%s%s\")",'https://nyscf.org/programs/extramural-grants/applicants/fellowship-awards', as.character('/')),
          sprintf("window.open(\"%s%s\")",'https://professional.diabetes.org/meetings/core-program', as.character('/')),
          sprintf("window.open(\"%s%s\")",'http://hhwf.org/research-fellowship', as.character('/')),
         # sprintf("window.open(\"%s%s\")",'https://www.hfsp.org/funding/hfsp-funding/postdoctoral-fellowships', as.character('/')) canada
          sprintf("window.open(\"%s%s\")",'https://www.asn-online.org/grants/fellowships', as.character('/')),
         sprintf("window.open(\"%s%s\")",'https://molssi.org/the-molssi-software-fellowship-program', as.character('/')),
         sprintf("window.open(\"%s%s\")",'https://www.niddk.nih.gov/research-funding/process/apply/funding-mechanisms/k-awards/k99-r00', as.character('/')),
         sprintf("window.open(\"%s%s\")",'https://www.aacr.org/professionals/research-funding/postdoctoral-and-clinical-research-fellow-grant-recipients', as.character('/')),
         sprintf("window.open(\"%s%s\")",'https://www.ctf.org/research/young-investigator-award-yia', as.character('/')),
         sprintf("window.open(\"%s%s\")",'https://www.abta.org/basic-research-fellowships', as.character('/')),
         sprintf("window.open(\"%s%s\")",'http://lalorfound.org/postdoctoral-fellowship-program', as.character('/')),
         sprintf("window.open(\"%s%s\")",'https://hria.org/tmf/KingBasic', as.character('/')),
         sprintf("window.open(\"%s%s\")",'https://www.hemophilia.org/Researchers-Healthcare-Providers/Research-Grant-Programs/Judith-Graham-Pool-Postdoctoral-Research-Fellowships', as.character('/')),
         sprintf("window.open(\"%s%s\")",'https://www.afar.org/research/funding/glenn-postdoc', as.character('/')),
         sprintf("window.open(\"%s%s\")",'https://www.apdaparkinson.org/research/research-opportunities/postdoctoral-research-fellowships', as.character('/')),
         sprintf("window.open(\"%s%s\")",'https://www.parkinson.org/research/information-for-researchers/early-career-fellowships/postdoctoral?_ga=2.7636154.908996889.1586645682-304117135.1586645682', as.character('/')),
         sprintf("window.open(\"%s%s\")",'https://www.pcf.org/science-impact/the-work-we-fund/young-investigator-awards', as.character('/')),
         sprintf("window.open(\"%s%s\")",'https://www.hdfoundation.org/funding-the-future-2', as.character('/')),
         sprintf("window.open(\"%s%s\")",'https://www.cff.org/Research/Researcher-Resources/Awards-and-Grants/Training-Awards/Postdoctoral-Research-Fellowship-Award', as.character('/')),
         sprintf("window.open(\"%s%s\")",'http://www.hope-funds.org/grants/eligibility-and-application', as.character('/'))

         
          # sprintf("window.open(\"%s%s\")",'https://www.hdfoundation.org/funding-the-future-2', as.character('/'))
          
),
'Deadline'=format(as.Date(c('07/01','02/03','10/01','08/15','07/20',
             '08/21','06/12','08/15','07/02','10/01',
            '01/08','11/16','07/15','12/02','10/01',
             '11/12','05/26','06/20','12/01','01/15',
             '03/04','NA','04/15','03/12','02/18',
             'NA','04/17','12/07','01/25'), format="%m/%d")),
'LOI'=format(as.Date(c('05/15','NA','NA','NA','05/05',
        '08/14','NA','NA','NA','NA',
        'NA','NA','NA','NA','NA',
        'NA','NA','01/03','11/01','NA',
        'NA','NA','01/22','NA','11/12',
        'NA','02/01','NA','09/18'), format="%m/%d")),
'Suitability'=c(70,100,95,85,25,
                45,25,75,45,80,
                95,65,85,35,45,
                20,90,25,30,30,
                95,15,95,15,15,
                30,20,30,90),

'fundingamount' = c(50000,54000,52000,55750,45000,
                    NA,66667,61040,45000,57000,
                    57500,55000,57000,50000,50000,
                    90000,75000,45250,50000,52000,
                    55000,52000,52000,50000,55000,
                    NA,75000,51000,52000),
'fundingduration' = c(2,3,3,4,3,
                      NA,3,2,3,3,
                      3,3,3,2,1,
                      2,3,2,2,2,
                      2,2,1,1,2,
                      NA,2,2,3),
'allowance' = c(0,3800,10000,2000,11250,
                7850,0,3000,5500,1500,
                2500,10000,1500,0,0,
                0,0,0,0,0,
                2000,0,8000,0,5000,
                NA,10000,9000,1500),

'success_rate'=c(NA,NA,2.7,NA,NA,
               NA,NA,43,NA,NA,
               NA,NA,5,NA,NA,
               29.7,NA,NA,NA,NA,
               20,NA,NA,NA,NA,
               NA,NA,NA,NA),
'it_per_year'=c(1,1,1,2,2,
              1,1,1,1,1,
              1,1,1,1,2,
              3,1,1,1,1,
              1,1,1,1,1,
              NA,1,2,1),
'comments' = c(NA,NA,NA,NA,NA,
               'salary and duration are requested during appliaction',
               'This Fellowship is not intended for individuals that already have completed a Ph.D. or students that have already identified a postdoctoral position and a postdoctoral mentor as traditional funding mechanisms are better suited to these students.   Such applications are ineligible for consideration.',
               NA,
               NA,
               NA,
               'New York area specific',
               NA,
               NA,
               NA,
               'collaboration with the MolSSI scientists',
               NA,
               NA,
               'YIA',
               NA,
               NA,
               NA,
               NA,
               NA,
               NA,
               NA,
               'YIA',
               NA,
               NA,
               NA
               )
#score = 

)

fellow2$truelink <- gsub("^.*?h","h",fellow2$Link)
fellow2$truelink <-substr(fellow2$truelink, 1, nchar(fellow2$truelink)-1) 


fellow2$fundingscore <- (100*fellow2$fundingamount)/max(fellow2$fundingamount, na.rm = T)
fellow2$durationscore <- (100*fellow2$fundingduration)/max(fellow2$fundingduration, na.rm = T)
fellow2$allownacescore <- (100*fellow2$allowance)/max(fellow2$allowance, na.rm = T)
fellow2$adjAwardsscore <- (100*fellow2$Awards_2019)/max(fellow2$Awards_2019, na.rm = T)

fellow2$score <- round(rowMeans(fellow2[c(7,7,7,7,7,15,16,17,18,18)], na.rm = T),digits = 2)

#fellow2$Deadline[is.na(fellow2$Deadline)] <-0 # as.Date('2020-01-01')
fellow2_1 <- NULL
fellow2_2 <- fellow2[is.na(fellow2$Deadline),]
fellow2 <- fellow2[!is.na(fellow2$Deadline),]

for (i in seq_along(fellow2$Fellowship)) {
 adjdates <- fellow2[i,]
 
 daaatee <- Sys.Date()
  if(daaatee > as.Date(adjdates$Deadline)){
    adjdates$Deadline <-  seq.Date(as.Date(adjdates$Deadline), length.out = 2, by = "year")[2]
  }
 fellow2_1 <- rbind.fill(fellow2_1, adjdates)
                        #  seq.Date(as.Date(adjdates$Deadline), length.out = 2, by = "year")[2], 
      #  as.Date(adjdates$Deadline))
  
}
fellow2_3 <- rbind.fill(fellow2_1,fellow2_2)

```


```{r table-fellow, echo=FALSE,warning = FALSE}
# dt <- fellow[1:6, 1:7]
# dt %>%
# mutate_all(as.character)
# 
# dim(dt)
# dt1 <- subset(dt, grepl("PhD", dt$Degree.Requirement) |grepl("Ph.D", dt$Degree.Requirement) )
# dt1 <- subset(dt1, grepl("None", dt1$Citizenship.Requirement) |grepl("visa", dt1$Citizenship.Requirement) | grepl("non-U.S.", dt1$Citizenship.Requirement) )
# dim(dt1)
fellow2_3 <- fellow2_3[order(as.Date(fellow2_3$Deadline)),]
fellow3 <- fellow2_3[c(1:3,5,6,7,8,9,10,19)]

my_palette <- colorRampPalette(c("red", "yellow", "green"))(n = 100)
#fellow3 <- sapply(1:nrow(fellow3), row_spec(background =factor(1:nrow(fellow3), fellow3$score,  my_palette[fellow3$score])))


 popover = spec_popover(
    content = fellow3$comment,
    title = NULL,                           # title will add a Title Panel on top
    position = fellow3$comment
  )

fellow3 %>% 
  mutate(Fellowship = cell_spec(fellow2_3$Fellowship, "html", link = fellow2_3$truelink #,color='black'
                                #,background = my_palette[fellow3$score]
                                ) ,
  #       Fellowship = spec_popover(
  #   content = fellow3$comment,
  #   title = NULL,                           # title will add a Title Panel on top
  #   position = fellow3$comment
  # ),
         score = cell_spec(score,background = my_palette[fellow3$score]),
       #   contact = cell_spec(contact,background = my_palette[fellow3$score]),
          Awards_2019 = cell_spec(Awards_2019,background = my_palette[fellow3$score]),
          Deadline = cell_spec(Deadline,background = my_palette[fellow3$score]),
          LOI = cell_spec(LOI,background = my_palette[fellow3$score]),
         Suitability = cell_spec(Suitability,background = my_palette[fellow3$score]),
        fundingamount = cell_spec(fundingamount,background = my_palette[fellow3$score]),
         fundingduration = cell_spec(fundingduration,background = my_palette[fellow3$score]),
          allowance = cell_spec(allowance,background = my_palette[fellow3$score]),

         
         ) %>%
  kable("html", escape = FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = T) %>%
   column_spec(1, bold = T, border_right = T) #%>%
 # cell_spec(score, bold = T, color = "white", background =factor(score, fellow3$score,  my_palette[fellow3$score]))




#dt %>%
#fellow3 <- fellow2$ %>% 
#  fellow2 <- mutate(fellow2, Fellowship = cell_spec(fellow2$Fellowship, link = fellow2$truelink,format = 'html'))
# 
# kableExtra::kable(fellow2,escape = T, format = 'html') %>%
#  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F) %>%
#    column_spec(1, bold = T, border_right = T)# %>%
# text_spec(fellow2$Fellowship, link = fellow2$truelink,format = 'html')
 
  #column_spec(5:7, bold = T) %>%
  #row_spec(3:5, bold = T, color = "white", background = "#D7261E")
 # add_header_above(c("a" = 5, "b" = 18)) %>%
 # kable_styling() #%>%
  #scroll_box(width = "100%", height = "200px")
#kable(fellow) %>%
#  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```


This is a list of postdoctoral fellowships for international postdocs in the USA (no citizenship/green card requirement). Each fellowship aims to fund mentored postdoctoral scholars who do biomedical research. I obtained the information about each fellowship from the fellowship website (Fellowship column). The obtained values are Fellowship Sponsor ("Fellowship"), Fellowships awarded in 2019 ("Awards_2019"), main email contact ("contact"), application submission deadline ("Deadline"), letter of intent deadline ("LOI"), a subjective suitability score (ranging from 0 - not suitable to 100 - very suitable) for basic cell cycle related research projects ("Suitability"), the funding amount/year ("fundingamount"), the maximum duration of the fellowship ("fundingduration"), the allowance funding ("allowance") and an overall score ("score", calculate by weighted 50% Suitability score, 30% funding score, 20% Fellowships awarded in 2019 score).  Fields that are 'NA' could not be obtained through the fellowship website.
The fellowships are ranked by date of deadline, from closest to furthest into the future. The highlighted colors represent the overall score from green (highest score), to yellow (intermeidate score), to red (lowest score).

```{r plotbox, echo=FALSE,warning = FALSE}

```


